RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-09-16 doc/paper.tex
Chapter 2: working

\documentclass[a4paper]{elsarticle}
% vim: tw=0 wm=0

\setcounter{tocdepth}{3}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{comment}
\usepackage{placeins}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
 \usepackage{booktabs}
\usepackage{array}
\usepackage[pdfencoding=auto,psdextra]{hyperref}
\usepackage{booktabs}
\usepackage{bookmark}% faster updated bookmarks
\usepackage{hypcap} % fix the links
\evensidemargin\oddsidemargin
\usepackage{graphicx}
\pagestyle{plain}
\usepackage{xcolor}
\newcommand\ToDo[1]{\textcolor{red}{#1}}
 \usepackage{tabularx}
\usepackage{xspace}
\usepackage{color}
\usepackage{epsfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
%\usepackage{changes}

\usepackage{blindtext}

@@

	 \begin{table}[!ht]
		\centering
		\scalebox{0.7}{
		\begin{tabularx}{450pt}{l  l  X}  
			Algorithm          &   Paper/year &   Short details   \\ \hline
			GP         &    \cite{koza1994genetic} (1994)    & Application of GP to SR \\ 
	        Hybrid GP  &   \cite{raidl1998hybrid} (1998)   & GP--based method; solutions locally optimizes by method of least squares to find optimum coefficients for top-level terms \\ 
	        DFE        & \cite{cerny2008using} (2008)   & Differential evolution algorithm \\
	        Eurequa                & \cite{schmidt2009distilling, schmidt2011machine} (2009, 2011) & Age-fitness pareto optimization approach using co-evolved fitness estimation   \\
        	APF            &      \cite{schmidt2010age} (2010)        &  Age-fitness pareto optimization approach                        \\
        	FFX  & \cite{mcconaghy2011ffx} (2011)  & The Fast Function Extraction algorithm --  non-evolutionary technique based on a machine learning technique called path-wise regularized learning \\
             ABCP &  \cite{karaboga2012artificial} (2012)  & Artificial bee colony programming  approach \\
			EPLEX          &      \cite{la2016epsilon} (2016)         &   A parent selection method called $\epsilon$--lexicase selection  \\ 
	       Local optimization     & \cite{kommenda2018local} (2018)   & Constants Optimization in GP by Nonlinear Least Square \\
	       SBP-GP &  \cite{virgolin2019linear} (2019)  & The idea of semantic back-propagation utilized in GP \\
	       BSR & \cite{jin2019bayesian} (2019) & ML--based approach; Bayesian symbolic regression  \\ 
	       DSR  & \cite{petersen2019deep} (2019) & Deep Symbolic Regression based on a RNN approach further utilizing the policy gradient search \\
	       OPERON & \cite{kommenda2020parameter} (2020) &  Utilizing nonlinear least squares for parameter identification of SR models with LS \\
	       VNP    & \cite{elleuch2020variable} (2020) & VNS based GP approach \\
	       OccamNet & \cite{costa2020fast} (2020) &   A fast neural network approach; the model defines a probability distribution over a non-differentiable function space; it samples functions and updates the weights with back-propagation  based on cross-entropy matching in an EA strategy	 \\

@@

Koza~\cite{koza1994genetic} introduced the problem of SR as a specific application of genetic programming. GP deals with the object called programs, which need to be optimized. In particular, the programs are represented by syntax trees consisting of functions/operations over input features and constants. \fxnote{TODO: dati primjer sintaksnog drveta} In essence, syntax trees are part of search space of SR. That is, each sample $\tilde{f}$ is a point in the search space, represented by respective syntax tree. How accurate is this mapping, we compute in the basis of the historical data $D$ and the chosen error   measure (such as $MSE$, or $R^2$).

>>>>

\documentclass[a4paper,12pt]{elsarticle}
% vim: tw=0 wm=0

\setcounter{tocdepth}{3}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{comment}
\usepackage{placeins}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
 \usepackage{booktabs}
\usepackage{array}
\usepackage[pdfencoding=auto,psdextra]{hyperref}
\usepackage{booktabs}
\usepackage{bookmark}% faster updated bookmarks
\usepackage{hypcap} % fix the links
\evensidemargin\oddsidemargin
\usepackage{graphicx}
\pagestyle{plain}
\usepackage{xcolor}
\newcommand\ToDo[1]{\textcolor{red}{#1}}
 \usepackage{tabularx}
\usepackage{xspace}
\usepackage{color}
\usepackage{epsfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
%\usepackage{changes}
\usepackage{tikz}
\usepackage{fullpage}
\usepackage{calc}
\usetikzlibrary{positioning,shadows,arrows,trees,shapes,fit}
\usepackage{blindtext}

@@

	 \begin{table}[!ht]
		\centering
		\scalebox{0.7}{
		\begin{tabularx}{550pt}{l  l  X}  
			Algorithm          &   Paper/year &   Short details   \\ \hline
			GP         &    \cite{koza1994genetic} (1994)    & Application of GP to SR \\ 
	        Hybrid GP  &   \cite{raidl1998hybrid} (1998)   & GP--based method; solutions locally optimizes by method of least squares to find optimum coefficients for top-level terms \\ 
	        DFE        & \cite{cerny2008using} (2008)   & Differential evolution algorithm \\
	        Eurequa                & \cite{schmidt2009distilling, schmidt2011machine} (2009, 2011) & Age-fitness pareto optimization approach using co-evolved fitness estimation   \\
        	APF            &      \cite{schmidt2010age} (2010)        &  Age-fitness pareto optimization approach                        \\
        	FFX  & \cite{mcconaghy2011ffx} (2011)  & The Fast Function Extraction algorithm --  non-evolutionary technique based on a machine learning technique called path-wise regularized learning \\
             ABCP &  \cite{karaboga2012artificial} (2012)  & Artificial bee colony programming  approach \\
			EPLEX          &      \cite{la2016epsilon} (2016)         &   A parent selection method called $\epsilon$--lexicase selection  \\ 
	       Local optimization     & \cite{kommenda2018local} (2018)   & Constants Optimization in GP by Nonlinear Least Square \\
	       SBP-GP &  \cite{virgolin2019linear} (2019)  & The idea of semantic back-propagation utilized in GP \\
	       BSR & \cite{jin2019bayesian} (2019) & ML--based approach; Bayesian symbolic regression  \\ 
	       DSR  & \cite{petersen2019deep} (2019) & Deep Symbolic Regression based on a RNN approach further utilizing the policy gradient search \\
	       OPERON & \cite{kommenda2020parameter} (2020) &  Utilizing nonlinear least squares for parameter identification of SR models with LS \\
	       VNP    & \cite{elleuch2020variable} (2020) & VNS based GP approach \\
	       OccamNet & \cite{costa2020fast} (2020) &   A fast neural network approach; the model defines a probability distribution over a non-differentiable function space; it samples functions and updates the weights with back-propagation  based on cross-entropy matching in an EA strategy	 \\

@@

Koza~\cite{koza1994genetic} introduced the problem of SR as a specific application of genetic programming. GP deals with the object called programs, which need to be optimized. In particular, the programs are represented by syntax trees consisting of functions/operations over input features and constants; as an example of a function represented by a syntax tree, see Figure~\ref{fig:syntax-tree-example} In essence, syntax trees are elements of the search space of SR. That is, each sample model $\tilde{f}$ may be seen as a point in the search space, represented by respective syntax tree. How accurate is this mapping, we compute in the basis of the historical data $D$ and the chosen error   measure (such as $MSE$, or $R^2$). \fxnote{TODO: proceed...}

\begin{figure}[!ht]
	\centering
\begin{tikzpicture}
	[font=\small, edge from parent, 
	every node/.style={top color=white, bottom color=blue!25, 
		rectangle,rounded corners, minimum size=6mm, draw=blue!75,
		very thick, drop shadow, align=center},
	edge from parent/.style={draw=blue!50,thick},
	level 1/.style={sibling distance=3cm},
	level 2/.style={sibling distance=1.2cm}, 
	level 3/.style={sibling distance=1cm}, 
	level distance=2cm,
	]
	\node (A) {$\times$} 
	child { node (B) {$\sin$}
		%child { node {x} 
			%edge from parent node[left=.5em,draw=none] {} }
		child { node {$x$}}
	}
	child {node (C) {$\times$}
		%child { node {x}
		%	child { node {C1a}}
		%}
		child { node {$x$}}
		child { node {$/$}
			child { node {$x$}}
			child { node {$y$} %edge from parent node[right=.5em,draw=none] {$\frac{a}{b}$}
			}
		}
	};
%	child { node {+} 
	%	child { node {2}}
	%	child { node {$x$}}
	%};

\end{tikzpicture}

\caption{Syntax tree representation for the expression $\sin x \times   ( x \times  x / y  )  = \frac{x^2 \sin x }{y}$}
\label{fig:syntax-tree-example}
\end{figure}
